A modelling strategy to improve cacao quality and productivity

### 2021-10-07 papers/model/paper_model.tex
Update paper_model.tex

% Authors, for the paper (add full first names)
\Author{Angela Romero V $^{1,\dagger,\ddagger}$\orcidA{}, Adriana Gallego $^{1,\ddagger}$ and Anyela V. Camargo R.$^{1,}$*}

@@

% Affiliations / Addresses (Add [1] after \address if there is only one affiliation.)
\address{%
$^{1}$ \quad The John Bingham Laboratory, NIAB, 93 Lawrence Weaver Road, Cambridge CB3 0LE, UK 1; e-mail@e-mail.com\\
$^{2}$ \quad BIOS 2; e-mail@e-mail.com}

% Contact information of the corresponding author
\corres{Correspondence:anyela.camargorodriguez@niab.com; Tel.: (optional; include country code; if there are multiple corresponding authors, add author initials) +xx-xxxx-xxx-xxxx (F.L.)}

% Current address and/or shared authorship
\firstnote{Current address: Affiliation 3} 
\secondnote{These authors contributed equally to this work.}
% The commands \thirdnote{} till \eighthnote{} are available for further notes

>>>>

% Authors, for the paper (add full first names)
\Author{Angela Romero V $^{1,\dagger,\ddagger}$*\orcidA{}, Adriana Gallego $^{2}$ and Anyela V. Camargo R.$^{1, \ddagger}$}

@@

% Affiliations / Addresses (Add [1] after \address if there is only one affiliation.)
\address{%
$^{1}$ \quad The John Bingham Laboratory, NIAB, 93 Lawrence Weaver Road, Cambridge CB3 0LE, UK 1}\\ %e-mail@e-mail.com\\
$^{2}$ \quad BIOS Colombia}%; e-mail@e-mail.com}

% Contact information of the corresponding author
\corres{Correspondence: angela.romerovergel@niab.com} %; Tel.: (optional; include country code; if there are multiple corresponding authors, add author initials) +xx-xxxx-xxx-xxxx (F.L.)}

% Current address and/or shared authorship
%\firstnote{Current address: Affiliation 3} 
\secondnote{These authors contributed equally to this work.}
% The commands \thirdnote{} till \eighthnote{} are available for further notes
